Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-08 Ben_Manuscripts/transport/Supporting_Information.tex
added a couple of comments/corrections.

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails in addition to a water reservoir between periodic images. We filled
  the pores with water by running \texttt{gmx solvate} on our initial
  configuration and removing any water molecules placed in the tail region. The
  GROMACS command \texttt{gmx solvate} places water molecules in proximity to
  other atoms based on their van der waals radii and therefore does
  a decent job of preventing equilibration issues. This also means that the
  intial pore radius dictates the water content of the pore. We can however, put
  arbitrary amounts of water into the tail region. We chose to test systems with
  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
  given in Table~\ref{table:water_content}.

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
  \caption{Interactions between same-solutes are negligible when systems are 
  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
  molcules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interation}
  \end{figure}

@@

%  \clearpage
%  \section{Solute Pairing with Sodium}
%
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
%  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
%  the majority of the trapping occurence between 400 and 600 ns. Regions
%  highlighted red or blue indicate times when methanol's oxygen atom is within 
%  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
%  \end{figure}
%  
%  \section{Mercaptoethanol's range of behavior}
%  
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\linewidth]{SOH_trace.pdf}
%  \caption{}\label{fig:SOH_trace}
%  \end{subfigure}
%  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
%  to lengthy trapping. Large hops generally occur near the pore center while 
%  long entrapments occur while tangled among the monomer tails.}
%  \end{figure}
%  
%  \section{THF-sodium Complexation}
%  
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
%  \caption{Coordination of THF with sodium ions may help stabilize it inside the
%  pore region. For the first 700 ns of the trajectories shown, the center of mass
%  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
%  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
%  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
%  After 700 ns, THF separates from the sodium ion and moves closer to the head group
%  region.}\label{fig:thf_sodium_coordination}
%  \end{figure}
  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
  %this is physical or a force field artifact.
  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
  % solutes that we studied

@@

%  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq

@@

%  random walks on fractals (RWF) and fractional brownian motion (FBM).

@@

%  Based on the previous two sections, our model can likey be studied as a CTRW. 

@@

>>>>

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails in addition to a water reservoir between periodic images. We filled
  the pores with water by running \texttt{gmx solvate} on our initial
  configuration and removing any water molecules placed in the tail region. The
  GROMACS command \texttt{gmx solvate} places water molecules in proximity to
  other atoms based on their van der Waals radii and therefore does
  a decent job of preventing equilibration issues. This also means that the
  initial pore radius dictates the water content of the pore. We can however, put
  arbitrary amounts of water into the tail region. We chose to test systems with
  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
  given in Table~\ref{table:water_content}.

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
  \caption{Interactions between same-solutes are negligible when systems are 
  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
  molecules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interaction}
  \end{figure}

@@

%  \clearpage
%  \section{Solute Pairing with Sodium}
%
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
%  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
%  the majority of the trapping occurrence between 400 and 600 ns. Regions
%  highlighted red or blue indicate times when methanol's oxygen atom is within 
%  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
%  \end{figure}
%  
%  \section{Mercaptoethanol's range of behavior}
%  
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\linewidth]{SOH_trace.pdf}
%  \caption{}\label{fig:SOH_trace}
%  \end{subfigure}
%  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
%  to lengthy trapping. Large hops generally occur near the pore center while 
%  long entrapments occur while tangled among the monomer tails.}
%  \end{figure}
%  
%  \section{THF-sodium Complexation}
%  
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
%  \caption{Coordination of THF with sodium ions may help stabilize it inside the
%  pore region. For the first 700 ns of the trajectories shown, the center of mass
%  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
%  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
%  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
%  After 700 ns, THF separates from the sodium ion and moves closer to the head group
%  region.}\label{fig:thf_sodium_coordination}
%  \end{figure}
  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
  %this is physical or a force field artifact.
  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
  % solutes that we studied

@@

%  For Brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq

@@

%  random walks on fractals (RWF) and fractional Brownian motion (FBM).

@@

%  Based on the previous two sections, our model can likely be studied as a CTRW. 

@@

% LocalWords:  LLC solutes py solvated GROMACS mdp solute ctrw GitHub equil xtc
% LocalWords:  kinetically gro gmx solvate der Waals wt PR savename pl pr trr
% LocalWords:  plateaued xlinked BJC MSDs Gierer Wirtz MSD SE tamsds hbond dist
% LocalWords:  tetrose ribose glcyol png tortuosity nn methanol's THF ca Meroz
% LocalWords:  Mercaptoethanol's Mercaptoethanol Complexation complexation msd
% LocalWords:  Sokolov superdiffusion subdiffusion nojump ETH nboot RWF FBM npt
% LocalWords:  subdiffusive CTRWs traj fracshow nanopore RW hoppy ACF brownian
